External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-30 CVPR2017_Review_Unified.tex
add

\begin{figure}[t]
\centering
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
\end{minipage}
}
\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
\vspace{-2mm}
\label{fig4}
\end{figure}

@@

\subsection{Implementation Details}
Our proposed method contains two stages, the external prior learning stage and the external prior guided internal learning stage. In the first stage, we set $p = 6$ (so the patch size is $6\times 6 \times 3$), $M=10$ (the number of patches in a patch group (PG)), $W=31$ (so the window size for PG searching is $31\times31$, and $K=32$ (the number of Gaussians in Gaussian Mixture Model (GMM)). We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images. In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ5})), and $IteNum=4$ (the number of iterations for Alg. 1). Our proposed method needs about 60 seconds to denoise an image of size $512\times512\times3$ under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal"). The three methods perform denoising under the same framework as Equ. (\ref{equ5}). The "External" method employs the external dictionaries (i.e., $r=0$ in Equ. (\ref{equ5})) for denoising, while the "Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with internal dictionary learning (i.e., $r=3p^{2}$ in Equ. (\ref{equ5})). All parameters of the three methods are tuned to achieve corresponding best performance.

We compare the above mentioned three methods on the 60 cropped images from \cite{crosschannel2016}. The average PSNR results of these methods are listed in Table \ref{tab1}. It can be seen that our proposed method achieves higher PSNR results then the methods of "External" and "Internal". We also compare the visual quality of the images denoised by these methods. From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}). And by making use of both the external and internal priors, our proposed method can recover well both the structures and textures. Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}. Therefore the differences on PSNR and visual quality among the three methods are not influenced by the noise, but by the contents of the cropped images.

In summary, the proposed algorithm achieves better performance on denoising real noisy images than the external prior based method and internal prior based method.

\begin{table}
\caption{Average PSNR(dB) results of External, Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-2mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9691}
%\\
%\hline
\end{tabular}
\end{center}\vspace{-5mm}
\end{table}

\begin{table*}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab2}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
%\\
%\hline
%SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
\\
\hline
\end{tabular}
\end{center}\vspace{-5mm}
\end{table*}

@@

For the second dataset \cite{ncwebsite} with no "ground truth" images, we only compare the visual quality of the denoised images. Figure \ref{fig6} shows the denoised images of "Dog" by the competing methods. More visual comparisons can be found in the supplementary file. It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image. This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images. Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recovery real noisy images. However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.

>>>>

\begin{figure}[t]
\centering
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
\end{minipage}
}
\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
\vspace{-3mm}
\label{fig4}
\end{figure}

@@

\subsection{Implementation Details}
Our proposed method contains two stages, the external prior learning stage and the external prior guided internal learning stage. In the first stage, we set $p = 6$ (so the patch size is $6\times 6 \times 3$), $M=10$ (the number of patches in a patch group (PG)), $W=31$ (so the window size for PG searching is $31\times31$, and $K=32$ (the number of Gaussians in Gaussian Mixture Model (GMM)). We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images. In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ5})), and $IteNum=4$ (the number of iterations for Alg. 1). All experiments are performed under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal"). The three methods perform denoising under the same framework as Equ. (\ref{equ5}). The "External" method employs the external dictionaries (i.e., $r=0$ in Equ. (\ref{equ5})) for denoising, while the "Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Equ. (\ref{equ5})). All parameters of the three methods are tuned to achieve best performance.

We compare the above mentioned methods on the 60 cropped images from \cite{crosschannel2016}. The average PSNR and speed of these methods are listed in Table \ref{tab1}. It can be seen that our proposed method achieves better PSNR results than the methods of "External" and "Internal". The speed of our proposed method is much faster than the "Internal" method while a little slower than the "External" method. We also compare the visual quality of the denoised images by these methods. From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}). And by utilizing both the external and internal priors, our proposed method can recover well both the structures and textures. Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}. Hence, the differences on PSNR and visual quality among these methods only depends on the contents of the cropped images.

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  ?  & 706.63 & 58.47
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}

\begin{table*}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab2}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
%\\
%\hline
%SSIM & 0.8718  & 0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table*}

@@

For the second dataset \cite{ncwebsite} with no "ground truth" images, we only compare the visual quality of the denoised images. Figure \ref{fig6} shows the denoised images of "Dog" by the competing methods. More visual comparisons can be found in the supplementary file. It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image. This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images. Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recover real noisy images. However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.
